---
title: FAKE ZM Plots
output: pdf_document
---




```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
opts_chunk$set(echo = FALSE, warning = FALSE, 
               cache = FALSE, cache.path = "zm-plots-cache/", 
                fig.align = "center")
```


## Histograms 

## District Histograms of N Vaxxed per Week

```{r histograms}

include_graphics(
    "../data/output/plots/fake-district-histogram-bcg-week-plot.png")

```

## Town Histograms of N Vaxxed per Week per Vaccine

```{r town-histograms}

include_graphics(
    "../data/output/plots/fake-town-histogram-week.png")

```

## Calendar Time District Plots


```{r district-indiv-month}

include_graphics(
    "../data/output/plots/fake-district-calendar-facet-penta1-month-plot.png")
```

```{r district-facet-indiv-month}

include_graphics(
    "../data/output/plots/fake-district-vaccine-calendar-month.png")
```


```{r district-facet-month}

include_graphics(
    "../data/output/plots/fake-district-vaccine-calendar-month.png")
```




```{r district-calendar-month}

include_graphics(
    "../data/output/plots/fake-district-calendar-measles1-month-plot.png")
```


## Calendar Time Town Plots


```{r town-facet-calendar}

include_graphics(
    "../data/output/plots/fake-district-town-bcg-calendar-week-plot.png"
    )
```

```{r town-calendar-week}

include_graphics(
    "../data/output/plots/fake-town-calendar-measles1-week-plot.png")
```

```{r town-calendar-month}

include_graphics(
    "../data/output/plots/fake-town-calendar-measles1-month-plot.png")
```


## Event Time District Plots

```{r district-event-month}

include_graphics(
    "../data/output/plots/fake-district-event-time-measles1-month-plot.png")


```

## Event Time Town Plots

```{r town-event-month}

include_graphics(
    "../data/output/plots/fake-town-event-time-measles1-month-plot.png")


```

```{r town-event-week}

include_graphics(
    "../data/output/plots/fake-town-event-time-measles1-week-plot.png")


```


```{r district-town-facet-week}

include_graphics(
    "../data/output/plots/fake-district-town-penta3-event-time-month-plot.png"
)
```


Maybe instead of plotting town lines we should plot points and bin them - 
but then might as well just show district/month??


# Event Study Plots

### What am I looking at?

Event study estimates calculated using Callaway and Sant'Anna. I.e. we estimate 
$ATT(g, t)$ for each time period and town and aggregate these into event time. 
Standard errors are clustered at the district level but estimates use town level 
data. 

The month level plot collapses N vaccinations into number of vaccinations in each 
town per month and sets the treatment time to the first of the month to 
avoid contamination. 

The week level plot collapses N vaccinations into number of vaccinations in each 
town per week. Treatment time is set to the first day of the week to avoid 
contamination.


I don't have enough RAM to run daily estimates using my laptop even with dummy data.

```{r town-es-month}

include_graphics(
    "../data/output/plots/fake-town-month-bcg-es-plot.png"
)
```


```{r town-es-week}

include_graphics(
    "../data/output/plots/fake-town-week-bcg-es-plot.png"
)


```