
\documentclass{article}

\setlength\textwidth{135.5mm}
\setlength\textheight{200mm}
\setlength\topmargin{-10pt}
\setlength\oddsidemargin{14mm}
\setlength\evensidemargin{\oddsidemargin}
\setlength\headheight{24pt}
\setlength\headsep   {14pt}
\setlength\topskip   {11.74pt}
\setlength\maxdepth{.5\topskip}
\setlength\footskip{15pt}



\title{Peer Review}
\author{Edward Jee}
\begin{document}
\maketitle



\section*{What I Liked}


The proposal clearly motivates the issue of agricultural technology adoption and 
how behavioural beliefs and social interactions could possibly lead to 
under-adoption. The focus on African countries, given technology adoption rates, 
is also clearly explained and even the choice of Angola in particular as a 
setting to study this problem.


I also like how the identification strategy attempts to isolate social norms 
from social learning. By focusing on harvests where farmers haven't observed 
crop yields but have potentially observed a different planting technique the 
proposal can tease out the effect of social norms. 

\section*{Points to address}


I have some points I think it'd be useful to think about, described below.


\subsubsection*{Choice of Angola}
As raised in the presentation, it would be good to investigate why Angola in 
particular has such low crop yields. It seems plausible there could be other, 
more immediate issues driving low yields and perhaps social norms could be 
better studied in another setting which we understand better?



\subsubsection*{Choice of training levels}

Currently, the control group has 10\% of farmers trained and the treatment group 
has 80\%. My understanding is that we want to shift social norms so create a 
treatment group with majority of farmers trained and a control group with a 
minority. However, it's not clear to me that social norms will only shift if we 
have $>50$\% of farmers trained - in some sense it could be easier to detect 
effects in the control group since we observe 90\% of the sample that could 
swap technology but only 20\% of the sample in the treatment group can be 
influenced.

Therefore, you probably want to think about a model/write down the dynamics of
social norm formation and figure out just how much fraction of farmers should 
be trained. If this is an open empirical question we don't have an answer to, 
why not create three treatment groups and vary training percentages from 25\% to 
75\% for instance. Power calculations would be useful here to figure just how 
to spread out the sample.



Finally, when we consider training levels it would be good to take figures from 
other studies to estimate takeup. For instance, social norms could be so strong 
that even trained farmers won't swap to the new technology and compliance will be 0. In this 
case, social norms are actually incredibly important but you'd estimate a null 
effect!




\subsubsection*{Training Design}

The training design could be motivated a little better I think. Maybe I missed 
this in the presentation but I don't quite follow why we'd train farmers for two 
weeks, observe harvesting decisions, and then train them for 16 weeks and observe 
harvesting decisions after yields have been observed for the first group. It 
seems like this design will create a intensive intervention for the social 
learning group but less of an intensive intervention for the social norms 
group?


Perhaps there's a good reason for this set-up or logistical constraints I'm missing?



\subsubsection*{Motivation for Norms vs Learning}
Finally, I understand that the goal is estimate the effects of social norms. However,
I think it's worth reflecting on why we want to do this in this context. If farmers 
can always observe yields after a few more months, does it matter that social norms
reduce technology adoption when, after observing results, social learning leads to 
large changes in takeup?

   
\section*{Summary}


I thought the proposal was very interesting and the presentation did a great job 
of focusing the audiences' minds on the important features of the problem. There's 
still some room to think about issues raised but overall very cool. 
\end{document}